Double White Dwarf Mergers on Adaptive Meshes\\ I. Methodology and Code Verification

### 2015-08-10 papers/wdmerger_I/paper.tex
Add the spatial convergence test to the paper.

>>>>

Finally we consider whether the dynamical behavior of the system converges with resolution. 
In \autoref{fig:unequal_spatial_convergence} we plot the first 10 seconds of the orbit for 
the unequal mass system, at three different resolutions in the inertial frame: our default 
resolution of $256^3$ zones, as well as a single level of refinement with a jump by a factor of 
two (effective resolution $512^3$) or a jump by a factor of four (effective resolution $1024^3$). 
It is clear that at the latter resolution (corresponding to physical resolution of 100 km), 
we have achieved convergent behavior. In the rotating frame (not shown here), the results are 
not quite the same but for these resolutions the results do tend toward convergence.

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{plots/spatial_convergence_rot0.eps}
  \caption{Distance between the two white dwarfs in the unequal mass system, for the first 
           10 seconds of their orbit. The distance is scaled by the initial orbital distance. 
           We plot at three different resolutions, corresponding to the number of 
           effective zones per dimension in the refined regions. Note that the $n = 1024$ curve
           falls nearly exactly on top of the $n = 512$ curve.\label{fig:unequal_spatial_convergence}}
\end{figure}
